Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2014-11-07 Paper/model.tex
Renamed Notes to paper folder.

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
{\tt\small vdhiman@nec-labs.com}
\and
Manmohan Chandraker\\
{\tt\small manu@nec-labs.com}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  The long term goal of this project is to identify and represent commonly 
  occurring potentially dangerous road situations where driver can be warned 
  about the situations. Such kind of driver assistance requires understanding
  the state of various road scene elements. We broadly categorize the elements
  in the scene as traffic participants (TP) and as other "scene elements" (like
  lanes, intersections etc). 
\end{abstract}

>>>>

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
{\tt\small dhiman@umich.edu}
Manmohan Chandraker\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
{\tt\small jjcorso@eecs.umich.edu}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  TODO: Write abstract
\end{abstract}
